### 2021-04-22 input/background.tex
meow
background

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\REF. We advocate for the latter where
\processes host the service themselves so they do not need to request
remote -- possibly far away third-party -- entities to retrieve their
content location.  In this paper, we tackle the content indexing issue
as a logical partitioning problem. This section motivate this shift
and explains the shortcomings of existing implementations.

@@

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new content. \Process~$R$
can use uniform reliable broadcast~\REF and epidemic propagation~\REF
to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

@@

Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
creates a replica of this content. Similarly to \Process~$R$ and
\Process~$G$, \Process~$B$ can notify other \processes of this new
replica. However, the set of \processes that could actually use this
new replica is actually much smaller than the network size. Uniform
reliable broadcast is not designed for such context and would generate
a lot of unnecessary traffic. Instead, \processes need a communication
primitive that propagate notifications as long as \processes receiving
them consider them useful based on location information they carry. We
call such primitive \emph{scoped broadcast}, for messages transitively
reach a subset of interconnected \processes (the \emph{scope}) by
evaluating a predicate starting at its broadcaster (the
\emph{source}). Using this primitive, \processes can lock down the
traffic of content indexing to relevant \processes.

@@

Every \process ends up with at least 1 known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
\processes to communicate with based on metrics~\REF, \processes in
our context have no control over their neighboring \processes.

@@

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belong to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partition would block the
propagation of other partitions.
\end{asparadesc}

Next Section details adaptive scoped broadcast in dynamic networks. It
details the properties of such protocol, and provides an
implementation along with its complexity.

>>>>

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\REF. We advocate for the latter where
\processes host the service themselves so they do not need to request
remote -- possibly far away third-party -- entities to retrieve their
content location.  In this paper, we tackle the content indexing issue
as a dynamic logical partitioning problem. This section motivates this
shift and explains the shortcomings of existing implementations.

@@

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new content. \Process~$R$
can use uniform reliable broadcast~\REF and epidemic propagation~\REF
to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

@@

Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
creates a replica of this content. Similarly to \Process~$R$ and
\Process~$G$, \Process~$B$ can notify other \processes of this new
replica. However, the set of \processes that could actually use this
new replica is actually much smaller than the network size. Uniform
reliable broadcast is not designed for such context and would generate
a lot of unnecessary traffic. Instead, \processes need a communication
primitive that propagates notifications within a scope by evaluating a
predicate, starting at its broadcaster (the \emph{source}).
In other terms, \processes propagate these notifications as long as they
consider them useful based on location information they carry. We call
such primitive \emph{scoped broadcast}, for messages transitively
reach a subset of interconnected \processes (the \emph{scope})
Using this primitive, \processes can lock down the traffic of content
indexing to relevant \processes.

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
neighboring \processes to communicate with based on metrics~\REF,
\processes in our context have no control over their neighboring
\processes: they cannot add nor remove communication links.

@@

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belonged to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions.
\end{asparadesc}

Next Section details the properties of adaptive scoped broadcast in
dynamic networks, and provides an implementation along with its
complexity.
